---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# choosy

The ideal of this package is to get some practice with optimization algorithms to fit **multinomial logistic regression** models.

# To Do / Roadmap

1. Gradient descent in R
1. Calling Rcpp/Python code
1. L-BFGS
1. Newton's method
1. ADMM
1. Line/beam search for step size

Eventually we may want the following methods:

* accept `recipe` objects?
* `tidy` method
* `augment` method
* `plot` method

# Installation

Once we get underway, you'll be able to install this package with:

```{r, results = 'hide'}
# install.packages('devtools')
# devtools::install_github('alexpghayes/choosy')
```

# Motivation

...

## Assumptions

* Independence of Irrelevant Alternatives: what it is, and what are some options to get around it, where those are implemented in R (i.e. `mlogit`)
* What type of data you have: data about observed individuals rather than alternatives to select from
* Other

# Example Usage

...
